---
title: "Desire to enhance analyst skillset prior to entering the job market"
author: "Andrew Nalundasan"
date: "October 15, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
n_employees <- 40
n_days <- 'four'
data_viz <- '5210'
weekly_hours <- 20
```

## Statement of interest 

As I progress through the MS in Business Analytics (MSBA) program, I find myself craving real-world experience within the data science industry. Being midway through the MSBA program, I have begun my due diligence of putting out feelers for work once I complete the program in August 2022. In order to enhance my competitiveness in the job market, I am striving to gain relevant experience as an analyst. I would apply the experiences from this fellowship to my job search and have concrete insights to reference during job interviews. I am eager to explore the different avenues that the data science industry has to offer. Through my professional experience as a management consultant, I have come to know corporate America very well, which leaves me curious to learn more about the world of research and the private sector. 

I am motivated to do what it takes to continue my personal growth as a student and as a professional. This fellowship is the perfect opportunity for me to pursue as I have recently decided to leave my full-time consulting job to center my focus solely on completing the MSBA program. This positions me to commit to the `r weekly_hours` hours per week as described in the posting and allows me to put into practice the concepts that I have been learning through this program.

My goals and objectives through this fellowship would be to: 

1. Gain an immersive technical experience of working with data, R, and GitHub
2. Sharpen my statistical exploration and statistical interpretation acumen
3. Merge my management consultant background with my skills as an analyst
4. Hone my organization and communication skills
5. Grow my professional network

## Event management and research assistance experience

As a team lead at my previous employer, I helped coordinate an "all hands" meeting for all employees staffed to the firm's largest program. The event brought together `r n_employees` employees from across the country for face to face collaboration over `r n_days` days in Seattle. 

Responsibilities to manage this event entailed: 

+ Organization of travel logistics for traveling employees 
+ Communication with employees regarding schedule and expectations
+ Coordination with meeting venue 
    + Request bids from various hotels and event spaces
    + Room booking arrangements
    + Coffee, breakfast, lunch, dinner arrangements
    + A/V equipment, name tags, writing supplements
+ Planning of team building events throughout the week
+ Seek budget approvals from Program Director
+ Health and Safety point of contact for the event
+ Simultaneously maintain project progress and manage client expectations

I completed the MSBA `r data_viz` class in Data Visualization over the Summer 2021 quarter. In this class, I learned the principles of the Exploratory Data Analysis (EDA) process, how to construct effective visuals, and the art of telling stories with data. The example R code provided with this application was my midterm submission for the class, which walks through a full EDA of the sales trends of cereal companies and provides findings and actions formatted as a memo. Both documents were prepared in R Markdown and managed via GitHub in collaboration with my research partner.

## Conclusion

I appreciate your consideration for the Howard J. Bosanko Graduate Fellowship. If there are further questions regarding my qualifications, background, or motivation, I can be reached at analundasan@seattleu.edu. The link for the GitHub repository that was used to prepare this application is provided below. Thank you very much. 

Sincerely, 

Andrew Nalundasan

https://github.com/andrewn488/Grad_Fellowship_Bosanko.git

